Case study validations of automatic bullet matching

### 2018-10-09 index.Rmd
lit review

XXX 3d technology

In the \svp{matching algorithm,} similarity of bullet land engraved areas is evaluated based on 3d topographic scans of land engraved areas (LEAs). From each land engraved area a signature is derived by

@@

What is quite surprising \svp{is} that what we anticipated to be the easiest case of Hamby 44 turned out to be the hardest to solve. This is likely due to several lands in the Hamby-44 set \svp{that have} major deficiencies,  such as 'tank rash' (a collision of the bullet after exiting the barrel with a surface causing markings on top of the striations from the barrel) or extreme pitting (holes caused by direct contact with burning gun powder).
\autoref{fig:tankrash} gives an overview of all lands of bullets in the Hamby-44 set affected. \svp{These issues affect the algorithm's ability to identify a stable signature, which impacts the subsequent match scores.}
```{r tankrash, fig.cap="Overview of bullet lands with prominent deficiency such as tank rash or extreme pitting in the Hamby-44 study.", fig.width=4, fig.height = 2, out.width='47.5%', fig.subcap=c("Br1-B1-L6", "Br2-B2-L5", "Br3-B1-L5", "Br8-B1-L6", "Br8-B2-L2", "Br8-B2-L6", "Unk-E-L6", "Unk-I-L6"), fig.align="middle", fig.ncol=2}
knitr::include_graphics(
  c(
    "./images/B1-B1-L6.png", "./images/B2-B2-L5.png",
    "./images/B3-B1-L5.png", "./images/B8-B1-L6.png",
    "./images/B8-B2-L2.png", "./images/B8-B2-L6.png",
    "./images/NA-BE-L6.png", "./images/NA-BI-L6.png"
  )
)
```

>>>>

## 3D Imaging Technology
\svp{3D characterization of bullet surfaces has been considered since 1958 \citeauthor{davis1968introduction}, but the technology was not sufficiently advanced for analysis based on 3D measurements to be a viable option. Approaches to utilizing 3D measurment data were proposed starting in 1999 \citeauthor{dekinderAutomatedComparisonsBullet1999}, and have been further developed by \citet{bachrachDevelopment3DbasedAutomated2002,xieAutomatedBulletidentificationSystem2009, chuPilotStudyAutomated2010}. These approaches utilize 3D surface measurements directly to characterize the topology of bullet surfaces, rather than using visual or image comparison techniques. In many cases, they also provide some level of automation of the comparison process, with the goal of reducing human biases by augmenting the visual information with 3D measurements. This allows for examination not only of the peaks in the bullet signature, but also for comparison of the valleys, which are more difficult to assess visually except in relation to the peaks. }

\svp{Commonly, approaches derived from 3D surface measurements use some features which are developed to mimic the perception of FTEs\citep{luAutomatedBulletIdentification2014}. Class characteristics, which are shared by a group of firearms with the same rifling design, manufacturer, and tooling process, are typically evaluated first, as a mismatch on class charcteristics is sufficient to conclude that two samples do not match. Automated approaches to estimation of width of the land engraved area and twist angle were described in \citet{chuPilotStudyAutomated2010}. Individual characteristics, which are not shared by all members of a class, can also be automatically assessed from 3D surface measurements; in some cases, these features mimic features used by FTEs during image analysis. One of the most common features used to assess the strength of a match based on individual characteristics is the cross-correlation function (ccf), which is described in several studies \citep{maNISTBulletSignature2004, vorburgerApplicationsCrosscorrelationFunctions2011, chuPilotStudyAutomated2010}. Additional features proposed for assessing match strength also include Signature Distance \citep{maNISTBulletSignature2004} and automatically determined Consecutive Matching Striae \citep{chuAutomaticIdentificationBullet2013}.}

### Need to transition to explanation of the match algorithm...
In the \svp{matching algorithm proposed in \citet{aoas},} similarity of bullet land engraved areas is evaluated based on 3d topographic scans of land engraved areas (LEAs). From each land engraved area a signature is derived by

@@

What is quite surprising \svp{is} that what we anticipated to be the easiest case of Hamby 44 turned out to be the hardest to solve. This is likely due to several lands in the Hamby-44 set \svp{that have} major deficiencies,  such as 'tank rash' (a collision of the bullet after exiting the barrel with a surface causing markings on top of the striations from the barrel) or extreme pitting (holes caused by direct contact with burning gun powder).
\autoref{fig:tankrash} gives an overview of all lands of bullets in the Hamby-44 set affected. \svp{These issues affect the algorithm's ability to identify a stable signature, which impacts the subsequent match scores.}
```{r tankrash, fig.cap="Overview of bullet lands with prominent deficiency such as tank rash or extreme pitting in the Hamby-44 study.", fig.width=4, fig.height = 2, out.width='47.5%', fig.subcap=c("Br1-B1-L6 (breakaway)", "Br2-B2-L5 (tank rash)", "Br3-B1-L5 (tank rash)", "Br8-B1-L6 (tank rash)", "Br8-B2-L2 (pitting)", "Br8-B2-L6 (breakaway)", "Unk-E-L6 (breakaway)", "Unk-I-L6 (breakaway)"), fig.align="middle", fig.ncol=2}
knitr::include_graphics(
  c(
    "./images/B1-B1-L6.png", "./images/B2-B2-L5.png",
    "./images/B3-B1-L5.png", "./images/B8-B1-L6.png",
    "./images/B8-B2-L2.png", "./images/B8-B2-L6.png",
    "./images/NA-BE-L6.png", "./images/NA-BI-L6.png"
  )
)
```
